Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with Uniform Kernels

### 2016-02-28 main_paper.tex
Make additional revisions to 'background' section

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}. We focus on the linear
  case for ease in exposition.} %
For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is
\begin{equation}
  \label{eq:13}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\beta} \sum_{i=1}^{N}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\beta} \sum_{i=1}^{N}
  \1\{0 > X_{i} > -h_n \} (Y_{i} - \beta_{0} - X_{i} \beta_{1})^{2}.
\end{align*}

As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions.\footnote{The assumptions below are the same as presented by CCT.}

\begin{assumption}[Bandwidth]\label{A2}
  Let $h_{n}$ be the bandwidth used to estimate the local linear model and let
  $b_{n}$ be the bandwidth used to estimate a local quadratic model. Then
  $n h_{n} \to \infty$, $n b_{n} \to \infty$, $n h_{n}^{5} b_{n}^{2} \to 0$, and
  $n b_{n}^{5} h_{n}^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.} %
  The relationship $h_{n} \leq b_{n}$ also holds for all $n$.
\end{assumption}

CCT point out that the conventional approaches to construct confidence intervals for $\tau$ using the local linear estimator rely on a large-sample approximation for the standardized $t$-statistic that is valid only if the bandwidth shrink fast enough to eliminate the leading bias term contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and $nh_{n}\rightarrow \infty$, then
 \begin{align}
  T(h_{n}) &=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), &
  V(h_{n}) &=\V(\tau(h_{n}) \mid X_{1},\dots,X_{n})
 \end{align}
 The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known quantities that depend on the kernel and order of polynomial used in the estimation. Under these conditions we could use a conventional confidence interval for $\tau$ given by
 \begin{align}
  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
 \end{align}
with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the standard normal distribution. However, most approaches to select the bandwidth, $h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a first-order bias in the distributional approximation used to construct the confidence intervals.

CCT solve the problem by deriving the analytical form of the first-order bias and correcting it directly. To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction. Their approach relies on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$. The approximate bias term can be described as:
\begin{align*}
     \E[\hat{\tau}(h_{n}) \mid \chi_{n}]-\tau=& h_{n}^{2}\Bs(h_{n})\{1+o_{p}(1)\}\\
     \Bs(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\Bf_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\Bf_{-}(h_{n})
   \end{align*}
where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$. The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,  using a (potentially) different pilot bandwidth $b_{n}$.
\begin{align*}
     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\\
     \hat{\Bs}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\Bf_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\Bf_{-}(h_{n})
   \end{align*}
By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\Bs}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general. So under Assumptions \ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
\begin{align}
  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1), \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
 \end{align}
where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed. The details can be found at CCT Appendix.}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
 \begin{align}
  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
 \end{align}

This approach is shown by the authors to significantly improve coverage of the CIs constructed and provides practitioners with a new tool set to perform inference that is more robust to the choice of bandwidth. We build upon the insight provided by CCT bias-corrected estimator and propose a simple bootstrap procedure that can directly construct the robust CIs without requiring the derivation of analytical formulas and direct estimators for the bias, variance and covariance terms, while relying on the same first-order bias correction approximation.

>>>>

Since the conditions for identification only need to hold in a neighborhood
around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
local polynomial regression.  We will focus here on local linear
regression.\footnote{%
  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
  the properties of local polynomial regressions for boundary problems. The
  bootstrap algorithm proposed in this paper can be extended to accommodate
  higher order polynomials discontinuities in the derivatives of the conditional
  expectation, like ``Kink RD'' design \citep{card2009b}. We focus on the linear
  case for ease in exposition.} %
For this model, if $h$ represents a bandwidth parameter, the estimator of
$\tau$, $\hat\tau(h)$, is
\begin{equation}
  \label{eq:13}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation}
with
\begin{align*}
  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
  &= \argmin_{\mu, \beta} \sum_{i=1}^{N}
  \1\{h > X_{i} \geq 0\} (Y_{i} - \mu - X_{i} \beta)^{2}
\intertext{and}
  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
  &= \argmin_{\mu,\beta} \sum_{i=1}^{N}
  \1\{0 > X_{i} > -h_n \} (Y_{i} - \mu - X_{i} \beta)^{2}.
\end{align*}
Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau$. In particular, if
\begin{gather}
  \label{eq:14}
  T(h) =\frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \to^p \plim \V(\tau(h) \mid X_{1},\dots,X_{n}),
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test. This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

However, the statistical properties of these estimators clearly depend on the
bandwidth parameter $h$, and bandwidths that have desirable properties for point
estimation may not have desirable properties for hypothesis testing or interval
estimation. In particular, for~\eqref{eq:14} to hold, $h$ must satisfy
$n h \to \infty$ and $n h^5 \to 0$. (\citealp{HTV2001}; \citealp{Porter03})
Otherwise, the finite-sample bias of $\hat\tau(h)$ does not converge in
probability to zero quickly enough and it contributes non-negligibly to the
asymptotic distribution~\eqref{eq:14}. This result holds even though
$\hat\tau(h)$ can be consistent under those conditions.  These bandwidth issues
are relevant in practice because many widely-used bandwidth selection
procedures, most notably the AMSE-optimal bandwidth and cross-validation
bandwidth \citep{IK} do not satisfy this condition.

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{gather*}
  \E(\hat{\tau}(h) \mid \chi_{n}) - \tau = h^{2}\Bs(h)\{1+o_{p}(1)\}
  \intertext{with}
  \Bs(h)=\tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h)
\end{gather*}
where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend
on the data, kernel, and bandwidth. The plug-in bias-corrected estimator then
requires estimates for the second derivatives of the conditional mean from above
and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that
these derivatives can be estimated by fitting a second order local polynomial,
i.e. one order higher than the polynomial used to obtain $\hat{\tau}$, using a
(potentially) different pilot bandwidth $b$. Their procedure gives the
bias-corrected estimator
\begin{gather*}
  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2} \hat{\Bs}(h,b)
  \intertext{with}
  \hat{\Bs}(h) = \tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h).
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation}
  T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h_{n}, b_{n})^{1/2}}
  \to^d N(0,1)
\end{equation}
with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term. This new approximation can be used
instead of~\eqref{eq:14} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples.

Assumption~\ref{A2} specifies the bandwidth conditions assumed by CCT, which we
will also use in this paper.
\begin{assumption}[Bandwidth]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.} %
  The relationship $h_{n} \leq b_{n}$ also holds for all $n$.
\end{assumption}

In the next section, we build upon the insight provided by CCT bias-corrected
estimator and propose a simple bootstrap procedure that can directly construct
the robust CIs without requiring the derivation of analytical formulas and
direct estimators for the bias, variance and covariance terms, while relying on
the same first-order bias correction approximation. The requirement $h < b$ is
new to this paper, because the bootstrap can not be implemented for the uniform
kernel without it, but the other parts of Assumption~\ref{A2} are taken from
CCT.
